DESING AND SIMULATION SOFTWARE FOR RHODOTRON TYPE ELECTRON ACCELERATORS

### 2023-09-19 subsections/design/magnet/magnet.tex
enstitü versiyonu

\section{Magnet Design} \label{sec:magnet_design}
Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
\iffalse \begin{figure}[H]
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/Ltot.png}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/tt300_mag.png}
    \end{subfigure}
    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300). \cite{cite:rhodo_design}}
    \label{fig:magnet_design_illustrations}
\end{figure} \fi
\begin{figure}[H]
    \centering
    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/design/Ltot.png} }}%
    \qquad\subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/design/tt300_mag.png} }}%
    \vspace{20pt}
    \caption{\centering Geometry and modeling, outside trajectory of a rhodotron (TT300). \cite{cite:rhodo_design}} 
    \label{fig:magnet_design_illustrations}
\end{figure}
In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for synchronizing them with the RF field in the cavity. 
This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
Time spent outside of the RF cavity should be precisely tuned to maximize acceleration in the succeeding pass.

@@

\begin{figure}[H]    
    \centering
    \includegraphics[width=.8\linewidth]{../../../figures/design/magnet_design.png}
    \caption{Trejectory of a particle in single pass.}
    \label{fig:magnet_design}
\end{figure}
From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, 
$L$ is the length of the magnet guide, $d$ is the thickness of the RF cavity wall the constraints are
\vspace{-10pt}\begin{eqnarray}
    L_{in} &=& 2R_2   , \nonumber\\
    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho  , \nonumber \\
    L_{pass} &=& L_{in} + L_{out}  ,  \nonumber \\
    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho . \label{eq:magnet_lambda_constraint}
\vspace{-10pt}\end{eqnarray}
After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
\vspace{-10pt}\begin{eqnarray}
    \tan (\gamma) &=& \frac{\rho}{R_2 + d + L}  , \nonumber \\
    \rho &=&  \tan (\gamma) (R_2 + d + L)  , \nonumber\\
    2\rho &=& \tan (\gamma) (\lambda - (\pi + 2\gamma)\rho)  , \nonumber\\
    \rho (2 + \tan (\gamma)(\pi + 2\gamma)) &=&  \tan (\gamma) \lambda   ,\nonumber\\
    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{\tan (\gamma)}}   ,\label{eq:magnet_rho_constraint} \\
    L + d &=& \frac{\rho}{\tan (\gamma)} - R_2 . \label{eq:magnet_L_constraint}
\vspace{-10pt}\end{eqnarray}

@@

Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
it can be observed that
\vspace{-10pt}\begin{eqnarray*}
    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV   ,\\
    W_{total} &=& 394 keV   ,\\
    \beta_{40keV} &\approx& 0.374   ,\\
    \beta_{394keV} &\approx& 0.825 .
\vspace{-10pt}\end{eqnarray*}
It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
\vspace{-10pt}\begin{eqnarray*}
    L_{pass} &=& K ,\\
    L_{in} + L_{out} &=& K .
\vspace{-10pt}\end{eqnarray*}
Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
\vspace{-10pt}\begin{equation} \label{eq:mag_sweep_constraint}
    L_{out} = K .
\vspace{-10pt}\end{equation}
To start, an optimization criteria for the following pass such as
\begin{itemize}
    \item Ensure the phase stability of the synchronous electron
    \item Maximize the energy gain of the synchronous electron
    \item Minimize the energy spread of the beam
    \item Minimize the phase lag spread of the beam
    \item All of the above with decided weights
\end{itemize}
needs be selected. Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.

>>>>

\section{Magnet Design} \label{sec:magnet_design}
Magnet design in rhodotron type accelerators depend heavily on the design of the cavities.
Because the limiting factors usually are frequency and total volume of the accelerator, magnet design parameters are considered after cavity design has been completed.
Considering the nature of coaxial cavity, simplest path for beams inside magnets is major segment of a circle, which was used as the reference for following discussions.
\iffalse \begin{figure}[H]
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/Ltot.png}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.9\linewidth]{../../../figures/design/tt300_mag.png}
    \end{subfigure}
    \caption{Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}.}
    \label{fig:magnet_design_illustrations}
\end{figure} \fi
\vspace{20pt}
\begin{figure}[H]
    \centering
    \subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/design/Ltot.png} }}%
    \qquad\subfigure[\centering ]{{\includegraphics[width=.45\textwidth]{../../../figures/design/tt300_mag.png} }}%
    \vspace{20pt}
    \caption{\centering Geometry and modeling, outside trajectory of a rhodotron (TT300) \cite{cite:rhodo_design}.} 
    \label{fig:magnet_design_illustrations}
\end{figure}
In rhodotron accelerators, magnets are used for not only guiding the electron beam to desired path, but also for synchronizing them with the RF field in the cavity. 
This syncronization, also called phase stability, is the fundamental constraint of magnet design. 
Time spent outside of the RF cavity should be precisely tuned to maximize acceleration in the succeeding pass.

@@

\begin{figure}[H]    
    \centering
    \includegraphics[width=.8\linewidth]{../../../figures/design/magnet_design.png}
    \vspace{20pt}
    \caption{Trejectory of a particle in single pass.}
    \label{fig:magnet_design}
\end{figure}
\clearpage
From \fromfig{magnet_design}, where $\gamma$ is half the angle between trajectories of successive passes, $\rho$ is the radius of the circular path inside magnet, 
$L$ is the length of the magnet guide, $d$ is the thickness of the RF cavity wall the constraints are
\vspace{-10pt}\begin{eqnarray}
    L_{in} &=& 2R_2   , \\
    L_{out} &=& 2L + 2d + (\pi + 2\gamma)\rho  , \\
    L_{pass} &=& L_{in} + L_{out}  ,   \\
    \lambda &=& 2R_2 + 2d + 2L + (\pi + 2\gamma)\rho . \label{eq:magnet_lambda_constraint}
\vspace{-20pt}\end{eqnarray}

After the cavity design is complete, only $L$, $\gamma$ and $\rho$ remain, which are the design parameters of magnets.
Observing the \fromfig{magnet_design} and using \fromeq{magnet_lambda_constraint},
\vspace{-10pt}\begin{eqnarray}
    \tan (\gamma) &=& \frac{\rho}{R_2 + d + L}  ,\\
    \rho &=&  \tan (\gamma) (R_2 + d + L)  , \\
    2\rho &=& \tan (\gamma) (\lambda - (\pi + 2\gamma)\rho)  , \\
    \rho (2 + \tan (\gamma)(\pi + 2\gamma)) &=&  \tan (\gamma) \lambda   ,\\
    \rho &=& \frac{\lambda}{\pi + 2\gamma + \frac{2}{\tan (\gamma)}}   ,\label{eq:magnet_rho_constraint} \\
    L + d &=& \frac{\rho}{\tan (\gamma)} - R_2 . \label{eq:magnet_L_constraint}
\vspace{-20pt}\end{eqnarray}

@@

Consider an RF supply with $f=1$ GHz, $P=50$ kW. Using \fromeq{W_total_gain_pottier}, 
after the first pass the synchronous electron that entered the accelerator with $40$ keV and $\phi=15^\circ$ phase lag,
it can be observed that
\vspace{-10pt}\begin{eqnarray}
    W_{gain} &=& 2.14\times0.2998^{1/4}\times 50000^{1/2} = 354keV   ,\\
    W_{total} &=& 394 keV   ,\\
    \beta_{40keV} &\approx& 0.374   ,\\
    \beta_{394keV} &\approx& 0.825 .
\vspace{-20pt}\end{eqnarray}
It is clear that $\beta_{avg}$ is not fast enough to sustain phase stability if the magnet is designed for $\beta = 1$. 
For these cases, \fromeq{magnet_lambda_constraint} fails to deliver phase stability.
Another approach for designing a magnet would be to find a new constraint, $K$ for total path length.
\vspace{-10pt}\begin{eqnarray}
    L_{pass} &=& K ,\\
    L_{in} + L_{out} &=& K .
\vspace{-20pt}\end{eqnarray}
Since $L_{in}$ is set previously from cavity design, we can remove it from our equation and continue with
\vspace{-10pt}\begin{equation} \label{eq:mag_sweep_constraint}
    L_{out} = K .
\vspace{-10pt}\end{equation}
\clearpage
To start, an optimization criteria for the following pass such as
\vspace{-10pt}
\begin{itemize}
    \item Ensure the phase stability of the synchronous electron
    \item Maximize the energy gain of the synchronous electron
    \item Minimize the energy spread of the beam
    \item Minimize the phase lag spread of the beam
    \item All of the above with decided weights
\vspace{-10pt}\end{itemize}
needs be selected. Using a simulation software such as \textit{CST Studio Particle Module}, the optimum value of $K$ for the criteria can be found by simulating for different values of $K$ (\textit{sweeping}) and analyzing the results.
This process can be repeated for each magnet until the desired beam characteristics in the end of the accelerator are achieved.

### 2023-09-19 subsections/future/future_work.tex
push for sina1
enstitü versiyonu

\documentclass[a4paper,oneside,12pt]{report}
\usepackage{amsmath, amsthm} % Some extra symbols
\usepackage[bottom]{footmisc}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{amssymb,bm,cite,graphicx, fixmath, texdraw}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{notoccite}
\usepackage{subcaption}
\usepackage{tabu}

@@

\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
Several improvements and new feature implementations are underway in the meantime. 
They include the following;
\begin{figure}[H]
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Electric and magnetic field import
            \item Field generator module to directly produce field files from specified cavity
            \item Synchrotron radiation calculations to determine radiation and energy loss
            \item \ee interactions
            \item Redesign of the GUI
            \item 3D render in GUI
        \end{itemize}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Refactoring of the \eEM interaction and logging to improve performance
            \item Refactoring of the GUI Render Frame to improve render speed
            \item Refactoring the magnet class to introduce field leaks
            \item Extention of analysis tools in Analyze Frame
            \item $L_{out}$ sweep in Sweep Frame
        \end{itemize}
    \end{subfigure}
\end{figure}
After the cavity manufacturing is concluded, energy gain predictions of this software will be tested on this cavity. 
Complementary bending magnet design will be the first challange of \textit{Rhodotron Simulation}, which will provide tremendous testing and improvement opportunities.

>>>>

\documentclass[a4paper,oneside,12pt]{report}
\usepackage{amsmath, amsthm} % Some extra symbols
\usepackage[bottom]{footmisc}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{multirow}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{amssymb,bm,cite,graphicx, fixmath, texdraw}
\usepackage{epsfig}
\usepackage{epstopdf}
\usepackage{amsmath}
\usepackage{notoccite}
%\usepackage{subcaption}
\usepackage{caption}
\usepackage{subfigure}
\usepackage{tabu}

@@

\textit{Rhodotron Simulation}, which has been the main focus of this thesis, is ready and waiting to be tested with the cavity that is being manufactured; 
Several improvements and new feature implementations are underway in the meantime:
\iffalse \begin{figure}[H]
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Electric and magnetic field import
            \item Field generator module to directly produce field files from specified cavity
            \item Synchrotron radiation calculations to determine radiation and energy loss
            \item \ee interactions
            \item Redesign of the GUI
            \item 3D render in GUI
        \end{itemize}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{itemize}
            \item Refactoring of the \eEM interaction and logging to improve performance
            \item Refactoring of the GUI Render Frame to improve render speed
            \item Refactoring the magnet class to introduce field leaks
            \item Extention of analysis tools in Analyze Frame
            \item $L_{out}$ sweep in Sweep Frame
        \end{itemize}
    \end{subfigure}
\end{figure} \fi
\begin{figure}[H]
    \begin{minipage}[t]{0.5\textwidth}
        \begin{itemize}
            \item Electric and magnetic field import
            \item Field generator module to directly produce field files from specified cavity
            \item Synchrotron radiation calculations to determine radiation and energy loss
            \item \ee interactions
            \item Redesign of the GUI
            \item 3D render in GUI
        \end{itemize}
    \end{minipage}
    \begin{minipage}[t]{0.5\textwidth}
        \begin{itemize}
            \item Refactoring of the \eEM interaction and logging to improve performance
            \item Refactoring of the GUI Render Frame to improve render speed
            \item Refactoring the magnet class to introduce field leaks
            \item Extention of analysis tools in Analyze Frame
            \item $L_{out}$ sweep in Sweep Frame
        \end{itemize}
    \end{minipage}
\vspace{-10pt}\end{figure}

After the cavity manufacturing is concluded, energy gain predictions of this software will be tested on this cavity. 
Complementary bending magnet design will be the first challange of \textit{Rhodotron Simulation}, which will provide tremendous testing and improvement opportunities.

### 2023-09-19 subsections/production/manifacturing/mani.tex
enstitü versiyonu

Elastic version of the 304, 304L was chosen to be the production material for ease of bending.
These sheets were then pressed to achieve the shapes of the parts. 
Several flanges were then machined, including
\begin{itemize}
    \item $4.5$in EIA RF flange for RF input
    \item ISO-100KF vacuum connector flanges for vacuum pumps
    \item ISO-63 KF flange for probe insertion
    \item KF-40 flanges for beam line vacuum gauges
\end{itemize}
After desired shapes were produced inside surface of the sheets were polished with 2000 grits. 
304 stainless steel sheet bars of different sizes were then added by 
TIG welding to achieve pressure resistance.

Because the main body of the cavity was 5mm thick and 304L was used, deformations on cylinderical symmetry were encountered. 
This problem was solved by welding 6 10mm thick toroidal sheets between the coaxial cylinders, 
which would be removed after the heat treatment.
\begin{figure}
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg}
      \caption{Bottom part of the cavity while polishing.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/polish/rhodo_upper_polished_cropped.jpeg}
      \caption{Top part of the cavity after polishing.}
    \end{subfigure}
    \caption{Polishing of the inner surface of cavity.}
    \label{fig:manif_polishing}
\end{figure}

\begin{figure}
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg}
      \caption{Bottom part of the cavity with the exposed beam line in inner cylinder.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg}
      \caption{Bottom part of the cavity with the beam line assembled.}
    \end{subfigure}
    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
    \label{fig:manif_toroidal_sheets}
\end{figure}

\begin{figure}
    \captionsetup{justification=centering}
    \centering
    \includegraphics[width=.8\linewidth]{../../../figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
    \caption{Welded sheet bars.}
\end{figure}

\begin{figure}
    \captionsetup{justification=centering}
    \centering
    \includegraphics[width=.7\linewidth]{../../../figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
    \caption{Middle part of the cavity containing the beam line.}
\end{figure}

\begin{figure}
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/welding/rhodo_assembled_welding_cropped.jpeg}
      \caption{Welding sheet bars.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg}
      \caption{Welding toroidal sheets.}
    \end{subfigure}
    \caption{TIG welding.}
    \label{fig:manif_welding}
\end{figure}

\begin{figure}
    \captionsetup[subfigure]{justification=centering}
    \captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/assembled/rhodo_final_cropped_5.jpeg}
      \caption{Beam enter \& exit flanges.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/assembled/rhodo_final_4_cropped.jpeg}
      \caption{RF input \& probe flanges.}
    \end{subfigure}
    \caption{Flanges on the assembled cavity.}
    \label{fig:manif_assembled_flanges}
\end{figure}

\begin{figure}
    \captionsetup{justification=centering}
    \centering
    \includegraphics[width=.9\linewidth]{../../../figures/manif/assembled/rhodo_final_cropped.jpeg}
    \caption{Current stage of the cavity.}
    \label{fig:manif_assembled}
\end{figure}

>>>>

Elastic version of the 304, 304L was chosen to be the production material for ease of bending.
These sheets were then pressed to achieve the shapes of the parts. 
Several flanges were then machined, including
\begin{itemize}
    \item $4.5$in EIA RF flange for RF input,
    \item ISO-100KF vacuum connector flanges for vacuum pumps,
    \item ISO-63 KF flange for probe insertion,
    \item KF-40 flanges for beam line vacuum gauges.
\end{itemize}
After desired shapes were produced inside surface of the sheets were polished with 2000 grits. 
304 stainless steel sheet bars of different sizes were then added by 
TIG welding to achieve pressure resistance.

Because the main body of the cavity was 5mm thick and 304L was used, deformations on cylinderical symmetry were encountered. 
This problem was solved by welding 6 10mm thick toroidal sheets between the coaxial cylinders, 
which would be removed after the heat treatment.
\iffalse \begin{figure}
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg}
      \caption{Bottom part of the cavity while polishing.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/polish/rhodo_upper_polished_cropped.jpeg}
      \caption{Top part of the cavity after polishing.}
    \end{subfigure}
    \caption{Polishing of the inner surface of cavity.}
    \label{fig:manif_polishing}
\end{figure} \fi

\begin{figure}
    \centering
    \subfigure[\centering Bottom part of the cavity while polishing]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/polish/rhodo_bottom_unpolished_cropped.jpeg} }}%
    \qquad\subfigure[\centering Top part of the cavity after polishing]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/polish/rhodo_upper_polished_cropped.jpeg} }}%
    \vspace{20pt}
    \caption{Polishing of the inner surface of cavity.}
    \label{fig:manif_polishing}
\end{figure}

\iffalse \begin{figure}
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg}
      \caption{Bottom part of the cavity with the exposed beam line in inner cylinder.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg}
      \caption{Bottom part of the cavity with the beam line assembled.}
    \end{subfigure}
    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
    \label{fig:manif_toroidal_sheets}
\end{figure} \fi
\begin{figure}
    \centering
    \subfigure[\centering Bottom part of the cavity with the exposed beam line in inner cylinder]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/toroidal_sheets/rhodo_bottom_cropped.jpeg} }}%
    \qquad\subfigure[\centering Bottom part of the cavity with the beam line assembled]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/toroidal_sheets/rhodo_middle_toroidal_sheets_welded_cropped.jpeg} }}%
    \vspace{20pt}
    \caption{Deformation prevention measure, 10 mm thick toroidal sheets.}
    \label{fig:manif_toroidal_sheets}
\end{figure}

\begin{figure}
    %%\captionsetup{justification=centering}
    \centering
    \includegraphics[width=.8\linewidth]{../../../figures/manif/welding/rhodo_middle_sheetbars_cropped.jpeg}
    \vspace{20pt}
    \caption{Welded sheet bars.}
\end{figure}

\begin{figure}
    %%\captionsetup{justification=centering}
    \centering
    \includegraphics[width=.7\linewidth]{../../../figures/manif/toroidal_sheets/rhodo_middle_only_cropped.jpeg}
    \vspace{20pt}
    \caption{Middle part of the cavity containing the beam line.}
\end{figure}

\iffalse \begin{figure}
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/welding/rhodo_assembled_welding_cropped.jpeg}
      \caption{Welding sheet bars.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg}
      \caption{Welding toroidal sheets.}
    \end{subfigure}
    \caption{TIG welding.}
    \label{fig:manif_welding}
\end{figure} \fi
\begin{figure}
    \centering
    \subfigure[\centering Welding sheet bars]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/welding/rhodo_assembled_welding_cropped.jpeg} }}%
    \qquad\subfigure[\centering Welding toroidal sheets]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/welding/rhodo_middle_welding_toroidal_sheets_cropped.jpeg} }}%
    \vspace{20pt}
    \caption{\centering TIG welding.} 
    \label{fig:manif_welding}
\end{figure}

\iffalse \begin{figure}
    %\captionsetup[subfigure]{justification=centering}
    %\captionsetup{justification=centering}
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/assembled/rhodo_final_cropped_5.jpeg}
      \caption{Beam enter \& exit flanges.}
    \end{subfigure}%
    \centering
    \begin{subfigure}{.5\textwidth}
      \centering
      \includegraphics[width=.96\linewidth]{../../../figures/manif/assembled/rhodo_final_4_cropped.jpeg}
      \caption{RF input \& probe flanges.}
    \end{subfigure}
    \caption{Flanges on the assembled cavity.}
    \label{fig:manif_assembled_flanges}
\end{figure} \fi
\begin{figure}
    \centering
    \subfigure[\centering Beam enter \& exit flanges]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/assembled/rhodo_final_cropped_5.jpeg} }}%
    \qquad\subfigure[\centering RF input \& probe flanges]{{\includegraphics[width=.46\textwidth]{../../../figures/manif/assembled/rhodo_final_4_cropped.jpeg} }}%
    \vspace{20pt}
    \caption{\centering Flanges on the assembled cavity.} 
    \label{fig:manif_assembled_flanges}
\end{figure}

\begin{figure}
    %%\captionsetup{justification=centering}
    \centering
    \includegraphics[width=.9\linewidth]{../../../figures/manif/assembled/rhodo_final_cropped.jpeg}
    \vspace{20pt}
    \caption{Current stage of the cavity.}
    \label{fig:manif_assembled}
\end{figure}

### 2023-09-19 subsections/production/technical_drawings/techd.tex
enstitü versiyonu

%%%%%%
% Start of mani.tex
\section{Manifacturing}

%%%%%%

>>>>

%%%%%%
% Start of techd.tex
\section{Technical Drawing}
Technical drawings of the design mentioned in \fromsec{final_design} can be found in \fromfigs{techd_rhod}{techd_mid}, \fromfig{techd_up} of \fromapp{supp}.

\begin{figure}
    \centering
    \includegraphics[angle=270,origin=c, width=.95\linewidth]{../../../figures/teknikcizim/Rho-A1.0.00.pdf}
    \vspace{20pt}
    \caption{Technical drawing of the rhodotron cavity \cite{sinan}.}
    \label{fig:techd_rhod}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[angle=270,origin=c, width=.95\linewidth]{../../../figures/teknikcizim/Rhodotron Elektron Hizlandirici Sistemi.pdf}
    \vspace{20pt}
    \caption{Technical drawing of middle part of the cavity which contains the beam line \cite{sinan}.}
    \label{fig:techd_mid}
\end{figure}
%%%%%%

### 2023-09-19 subsections/simulation/gui/gui.tex
enstitü versiyonu

Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
\begin{figure}[H]
    \centering
    \includegraphics[width=0.95\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
    \caption{An Illustration of the first GUI design.}
    \label{fig:gui_illustration}
\end{figure}
This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.

@@

\newpage
\subsection{Configuration Frame}
This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_config_frame.png}
    \caption{The configuration frame of implementated first GUI design.}
    \label{fig:gui_config}
\end{figure}

\newpage
\subsection{Render Frame}
Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
see a specific time frame, export as snapshot or animated gif file.
Two example renders can be seen in \fromfig{gui_render_1} and \fromfig{gui_render_2} of \fromapp{supp}.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_render_frame_5.png}
    \caption{Render frame of \textit{GUI}.}
    \label{fig:gui_render_1}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_3.png}
    \caption{Analyze frame of \textit{GUI} E(t).}
    \label{fig:gui_analyze_Et}
\end{figure}

\newpage

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE_3.png}
    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ $\mu E$ result.}
    \label{fig:gui_sweep_muE}
\end{figure}
\newpage
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE_3.png}
    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ sweep $\sigma E$ result.}
    \label{fig:gui_sweep_sE}
\end{figure}

>>>>

Until this point, \textit{Rhodotron Simulation} could be used with a configration file, defining the problem that would be simulated.
An example of this configuration file can be found in \fromfig{config_file} of \fromapp{example_simulation_runs}. 
\begin{figure}[H]
    \centering
    \includegraphics[width=\linewidth]{../../../figures/illustrations/RhodoSim_GUI_Draft_V02.pdf}
    \vspace{20pt}
    \caption{An Illustration of the first GUI design.}
    \label{fig:gui_illustration}
\end{figure}
This approach was simple and fast; however, it was not suitable for the average target user since required basic knowledge of command line interface and was not up to modern standards.
For this reason, a GUI was decided to be built, using \textit{ROOT framework}. 
This would also enable \textit{Rhodotron simulation} to make use of analysis tools offered by \textit{ROOT}.

@@

\subsection{Configuration Frame}
This frame provides an interface for specifying, saving or loading a configuration, consists of $\vecthreeBF{B}$ field, $\vecthreeBF{E}$ field, \textit{RF} description, \egun, \textit{simulation} configuration regions.
Each one having an illustration of what the parameters are as can be seen in \fromfig{gui_config}.

\clearpage
\begin{figure}[h]
    \centering
    \includegraphics[width=\linewidth]{../../../figures/rhodoSim/GUI_config_frame.png}
    \vspace{20pt}
    \caption{The configuration frame of implementated first GUI design.}
    \label{fig:gui_config}
\end{figure}

\clearpage
\subsection{Render Frame}
Since the rendering capabilities of \textit{ROOT} is superior than \textit{gnuplot}, the user can render a playback of the simulation in real time, 
see a specific time frame, export as snapshot or animated gif file.
Two example renders can be seen in \fromfig{gui_render_1} and \fromfig{gui_render_2} of \fromapp{supp}.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_render_frame_5.png}
    \caption{Render frame of \textit{GUI}.}
    \label{fig:gui_render_1}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\linewidth]{../../../figures/rhodoSim/GUI_analyze_Et_3.png}
    \caption{Analyze frame of \textit{GUI} E(t).}
    \label{fig:gui_analyze_Et}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_muE_3.png}
    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ $\mu E$ result.}
    \label{fig:gui_sweep_muE}
\end{figure}
\clearpage
\begin{figure}[h]
    \centering
    \includegraphics[width=0.85\linewidth]{../../../figures/rhodoSim/GUI_sweep_sE_3.png}
    \caption{Sweep frame of \textit{GUI} $\phi_{lag}$ sweep $\sigma E$ result.}
    \label{fig:gui_sweep_sE}
\end{figure}
